Parity games in pushdown systems with parameters

### 2023-06-20 reachability/article.tex
up

{\bf Context}
Stack-based automata \textcolor{red}{pourquoi ne pas commencer directement avec lesPushdown systems ?}are a popular formalism for modeling the sequential behavior of computer programs. 
Pushdown systems \textcolor{red}{or stack-automata ?}are probably the most studied models of stack-based automata.
\textcolor{red}{inutile: They are
finite automata 
 extended with a stack that can be manipulated by pushing or popping stack symbols from some finite set, and can use the top of the stack to decide which transition to take next.}
\textcolor{blue}{ok je comprends que tu signales la différence mais c'est trop détaillé pour cet endroit du texte: To underline the fact that we are concerned with the graph of configurations and not the language recognized, we use the name pushdown system rather than pushdown automaton.}

@@

Games on the graphs of pushdown systems have been extensively studied.
It is known in particular from \cite{walukiewicz1996pushdown} that deciding the winner of a parity game on a graph of a pushdown system is an ${\sf EXPTIME}$-complete problem.
Several generalizations of the pushdown systems 
have been studied in depths, including
tree-pushdown systems \cite{guessarian1983pushdown}, ordered
multi-pushdown systems \cite{breveglieri1996multi, atig2012model}, annotated higher-order pushdown systems \cite{maslov1976multilevel, broadbent2012saturation}, and
strongly normed multi-pushdown systems \cite{czerwinski2012reachability}.

>>>>

% {\bf Context}

@@

Games on the graphs of pushdown systems have been extensively studied.
It is known in particular from \cite{walukiewicz1996pushdown} that deciding the winner of a parity game on a graph of a pushdown system is an ${\sf EXPTIME}$-complete problem.
Several generalizations of the pushdown systems 
have been studied in depths, including
tree-pushdown systems \cite{guessarian1983pushdown}, ordered
multi-pushdown systems \cite{breveglieri1996multi, atig2012model}, annotated higher-order pushdown systems \cite{maslov1976multilevel, broadbent2012saturation}, and
strongly normed multi-pushdown systems \cite{czerwinski2012reachability}.
\textcolor{blue}{ok je comprends que tu signales la différence mais c'est trop détaillé pour cet endroit du texte: To underline the fact that we are concerned with the graph of configurations and not the language recognized, we use the name pushdown system rather than pushdown automaton.}
